Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-20 outputs/paper/paper.Rmd
edit

# Introduction
Donald Trump won the 2016 United States presidential election. From what we remembered, it was quite surprising considering his image outside of U.S or even in U.S. Also, before the election, Hillary Clinton was ahead in most surveys as well. There is a famous quote that we learn from the past. We thought that even though we are living in 2022, it would be meaningful to analyze the election so that we get to know what U.S citizens thoughts, or in broader sense, thoughts trends in nowadays and what factors we considered most important to decide our representative.

This paper is mainly going to explore possible variables that potentially had impacts on decision regarding the election as well as their analysis. However, making a choice for choosing which variables affected U.S citizens to lean on Trump side or Clinton side was not easy because there is nothing in this world absolute. Thus, as we mentioned above, we are going to focus on general flows of results instead of defining variables as absolute factors of the demarcation. Following that, this paper has structures: Data, Results, Discussion, Appendix and supplementary survey.

@@

We mainly divided the variables into two parts: personal information (Age, race, gender, degree, born US and family income) and thoughts on national policies (national spending on education, race, arms, welfare, the poor, the other countries, social security and immigration).
As I mentioned above, deciding who to vote is followed by very complex system of thoughts. Thus, as we cut down the variables, they do not 100% guarantee of the vote. Also, we thought that excluding non-response completely would turn into a bias for our understandings in data, so even though it caused difficulties in interpretation, we decided to include it except "pres16", which is our main variable whether respondents voted for Clinton and Trump. This is because non-response does not have convey meaningful findings with respect to our interests.
There exists a survey similar to ours, CNN exit polls, however it is not easy to obtain the datasets they used. Also, US GSS is more realistic than exit polls since people would think more rational with sufficient time to think in US GSS than exit polls.

>>>>

# Introduction
Donald Trump won the 2016 United States presidential election. From what we remembered, it was quite surprising considering his image outside of U.S or even in U.S. Also, before the election, Hillary Clinton was ahead in most surveys as well. There is a famous quote that we learn from the past. We thought that even though we are living in 2022, it would be meaningful to analyze the election so that we get to know what U.S citizens thought, or in broader sense, thoughts trends in nowadays and what factors we considered most important to decide our representative.

This paper is mainly going to explore possible variables that potentially had impacts on decision regarding the election as well as their analysis. However, making a choice for  which variables affected U.S citizens to lean on Trump side or Clinton side was not easy because there is nothing in this world absolute. Thus, as we mentioned above, we are going to focus on general flows of results instead of defining variables as absolute factors of the demarcation. Following that, this paper has structures: Data, Results, Discussion, Appendix and supplementary survey.

@@

We mainly divided the variables into two parts: personal information (Age, race, gender, degree, born US and family income) and thoughts on national policies (national spending on education, race, arms, welfare, the poor, the other countries, social security and immigration).
As I mentioned above, deciding who to vote is followed by very complex system of thoughts. Thus, as we cut down the variables, they do not 100% guarantee of the vote. Also, we thought that excluding non-response completely would turn into a bias for our understandings in data, so even though it caused difficulties in interpretation, we decided to include it except "pres16", which is our main variable whether respondents voted for Clinton and Trump. This is because non-response does not have convey meaningful findings with respect to our interests.
There exists a survey similar to ours, CNN exit polls, however it is not easy to obtain the datasets they used. Also, US GSS is more realistic than exit polls since people would think more rational with sufficient time to think in US GSS than exit polls. Ext polls can show crucial factors, but it lackes the ability of general thoughts.
